Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-10 manuscript/paper.Rmd
update

-   importance of reproducibility
-   As a case on point ...?
-   Underscores the importance of reproducibility within the frame of
    statistical analysis. We use the study by to ... The current study
    builds on the paper by .. and starts in the manner of a replication
    study and extends the analyses therein. We focus on statistical
    analyses of these data and compare models based on varied
    specification of functional forms of the covariates.

@@

|-----------------|-----------------|--------------------------------------|

@@

>>>>

The clinical importance of systolic blood pressure (SBP) stands as a
cornerstone extensively acknowledged and documented across the continuum
of medical literature's data collection. Elevated SBP stands as an
precursor linked with a spectrum of critical health conditions, notably
encompassing cardiovascular disease, stroke, and renal impairment, among
others. This nexus between heightened SBP and these significant health
adversities underscores the gravity of SBP as a predictive marker for
adverse health outcomes. Noteworthy is the pivotal concern surrounding
the trajectory of SBP in the natural aging process, a trajectory
observed ubiquitously across diverse populations.

Within Western societies aged 40 years and above, a demonstrable pattern
emerges, revealing an approximate elevation of 7 mmHg in SBP per decade
[**CITE**]. This discernible and consistent increment in SBP with
advancing age accentuates its profound impact within the broader context
of aging-related health dynamics. Concurrently, diastolic blood pressure
(DBP), while demonstrating a concurrent rise correlating with age,
presents a substantially lower rate of increase when juxtaposed against
the ascending trajectory observed in SBP. Thus, in light of the
significance attached to SBP dynamics within aging populations and the
intricate interplay between age and blood pressure alterations, our
investigative focus is oriented towards the exploration of variables
that exert potential influence on systolic blood pressure (SBP). This
deliberate focus aims to elucidate the multifaceted nature of factors
contributing to SBP variability, enabling a more comprehensive
understanding of its determinants within the framework of health and
aging.

Beyond age, the basal metabolic rate (BMI) emerges as a recognized
contributor to systolic blood pressure (SBP), with individuals
exhibiting higher BMI values demonstrating a propensity for elevated
SBP. Gender also holds a discernible association with SBP dynamics.
Empirical evidence in CITE demonstrates that women typically manifest
lower SBP than men until the onset of menopause, after which women
exhibit higher SBP levels compared to men. Additionally, heightened
levels of cholesterol are closely linked to vascular damage. The
accumulation of cholesterol deposits and calcium within arteries
precipitates arterial stiffening, necessitating augmented cardiac
efforts to circulate blood, potentially culminating in elevated blood
pressure. This study endeavors to examine the interrelationships between
age and cholesterol levels, emphasizing consideration of potential
confounding variables. Table 1 comprehensively delineates the array of
variables under scrutiny, ensuring a comprehensive analysis of their
collective impact

@@

|------------------|------------------|-------------------------------------|

@@

\@article{Gurven_Blackwell_Rodríguez_Stieglitz_Kaplan_2012a, title={Does
blood pressure inevitably rise with age?}, volume={60},
url={[https://doi.org/10.1161/hypertensionaha.111.189100},](https://doi.org/10.1161/hypertensionaha.111.189100},)
DOI={[10.1161/hypertensionaha.111.189100](https://doi.org/10.1161/hypertensionaha.111.189100)},
number={1}, journal={Hypertension}, author={Gurven, Michael and
Blackwell, Aaron D. and Rodríguez, Daniel and Stieglitz, Jonathan and
Kaplan, Hillard}, year={2012}, month=jul, pages={25--33} }
